{\color{red} Arquitecturas de:}
\begin{itemize}
	\item {\color{red}\texttt{3G UMTS}}
	\item {\color{red}\texttt{3.5G}}
	\item {\color{red}\texttt{3.75G}}
	\item {\color{red}\texttt{3.9G}}
	\item {\color{red}\texttt{4G LTE}}
	\item {\color{red}\texttt{5G}}
\end{itemize}


\begin{thebibliography}{9}
\bibitem{tutorialspoint} 
Circuit Switching \href{https://www.tutorialspoint.com/circuit-switching}{https://www.tutorialspoint.com/circuit-switching}

\bibitem{datto} 
What’s The Difference Between Circuit vs. Packet Switching. \href{https://www.datto.com/library/whats-the-difference-between-circuit-vs-packet-switching}{https://www.datto.com/library/whats-the-difference-between-circuit-vs-packet-switching} 31 de Marzo, 2020.


\bibitem{tutorialspoint2} 
Packet Switching. \href{https://www.tutorialspoint.com/packet-switching}{https://www.tutorialspoint.com/packet-switching}



\bibitem{dallas} 
Packet Switching and Computer Networks. Prof Morat Torlak\\ \href{https://ece.utdallas.edu/~torlak/courses/ee4367/lectures/packet.pdf}{https://ece.utdallas.edu/~torlak/courses/ee4367/lectures/packet.pdf}.


\bibitem{comparitech} 
Circuit Switching vs Packet Switching: Differences, Advantages \& Disadvantages. \href{https://www.comparitech.com/net-admin/circuit-switching-vs-packet-switching/}{https://www.comparitech.com/net-admin/circuit-switching-vs-packet-switching/}. 26 de Junio, 2020.


\bibitem{tutorialspoint3} 
Message Switching. \href{https://www.tutorialspoint.com/message-switching}{https://www.tutorialspoint.com/message-switching}.


\bibitem{handoff} 
Handoff in Cellular Telecommunications. \href{https://www.geeksforgeeks.org/handoff-in-cellular-telecommunications/}{https://www.geeksforgeeks.org/handoff-in-cellular-telecommunications/}.

\bibitem{NCKU} 
``Wireless \& Mobile Networks'', NCKU. Prof. W.-G. Teng. 

\end{thebibliography}

